---
title: "The Impact of Far-Right Voting and Education on COVID-19 Vaccination Attitudes: A Multilevel Analysis"
subtitle: "AUSSDA hackathon -- Code & Visualisation"
author: "Ionel Matei & Sky Liu"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
runtime: shiny
knitr:
  opts_chunk:
    echo: true
    collapse: true
    out.width: "\\textwidth"
    attr.output: 'style="max-height: 200px"'
    tidy: 'styler'
---



### Section 1: Research question

We aim to investigate whether voting for far-right parties and years of education influence individuals' vaccination behaviors and attitudes during the COVID-19 pandemic. In this context, far-right parties have been manually selected by authors prior to the analysis. They are defined as those embracing right-wing populism and potentially extremist rhetoric, characterized by nationalism, anti-immigration sentiment, anti-establishment narratives, and intolerance toward minorities. These parties are distinguished from mainstream right-wing groups by their exclusionary ideologies and polarizing challenges to liberal democratic norms.  

Our data, sourced from the 10th round of the European Social Survey (ESS) face to face countries in 2020.



```{r setup r, warning=FALSE, message=FALSE}

options(repos = c(CRAN = "https://cran.r-project.org"))

p_needed <- 
  c("ggplot2", "viridis", "MASS", "optimx", "scales", "foreign", 
    "separationplot", "patchwork", "stargazer", "here", "dplyr", "formatR", "haven", "purrr", 
    "shiny", "shinythemes", "tidyverse", "rsconnect", "bs4Dash", "shinycssloaders", "sandwich", "lmtest", "shinycssloaders", "bs4Dash")

# Check installed packages and install any missing ones
packages <- rownames(installed.packages())
p_to_install <- p_needed[!(p_needed %in% packages)]
if (length(p_to_install) > 0) {
  install.packages(p_to_install)
}

# Load the required packages
sapply(p_needed, require, character.only = TRUE)

# Set theme for ggplot2
theme_set(theme_classic() + 
  theme(
    plot.background = element_blank(),
    plot.title.position = "plot",  
    legend.position = "bottom" 
  ))

set.seed(1485)

```



### Section 2: Data cleaning

We conducted a thorough data cleaning process. First, we manually identified far-right parties in each country (definition see Section 1) and created a binary variable indicating whether respondents voted for such parties (coded as 1) or for other parties (coded as 0). 



```{r Data cleaning 1, warning=FALSE}
data <- read.spss(paste0("ESS10-subset/ESS10-subset.sav"), use.value.labels = F, use.missings = F, to.data.frame = T) %>% 
  as_tibble 

# List of valid country codes
valid_countries <- c("BE", "BG", "CH", "CZ", "EE", "FR", "FI", "GB", "GR", "HR", "HU", "IT", "LT", "ME", "MK", "NL", "NO", "PT", "SI", "SK")

# Filter the data to retain only rows with valid country codes
data <- data[data$cntry %in% valid_countries, ]


# List of far-right values for each country
far_right_parties <- list(
  prtvtebe = c(6),                     # Belgium
  prtvtebg = c(8, 9),                  # Bulgaria
  prtvthch = c(1, 9, 10),              # Switzerland
  prtvtbhr = c(3),                     # Croatia
  prtvtecz = c(8),                     # Czechia
  prtvthee = c(6),                     # Estonia
  prtvtefr = c(11),                    # France
  prtvtdgr = c(7),                     # Greece
  prtvtghu = c(4),                     # Hungary
  prtvtdit = c(3, 5, 10),              # Italy
  prtvthnl = c(3, 13),                 # Netherlands
  prtvtdno = c(8),                     # Norway
  prtvtdpt = c(4),                     # Portugal
  prtvtdsi = c(8, 11),                 # Slovenia
  prtvtesk = c(4),                     # Slovakia
  prtvtdgb = c(7, 8)                   # United Kingdom
)

# Initialize a new column for the unified far-right dummy with 0
data$far_right_dummy <- 0

# Iterate through the list and mark the dummy as 1 if a far-right party is matched
for (party_var in names(far_right_parties)) {
  if (party_var %in% names(data)) {
    data$far_right_dummy <- ifelse(
      data[[party_var]] %in% far_right_parties[[party_var]],
      1,
      data$far_right_dummy
    )
  }
}


```



Additionally, invalid responses such as "Refusal," "Don’t know," and "No answer" in subjective questions were excluded. We categorized participants’ vaccination intentions using the ESS survey questions "getavc19" and "getnvc19." Responses were grouped into three categories:

- **Yes, Vaccinated or Willing**: Included those who selected "Yes, I will," "Yes, I already have," or "Yes, I would."
- **No/Refused to answer**: Included those who selected "No," "Refusal," or "No, I would not."
- **Undecided**: Included responses such as "Not applicable," "Don’t know," or "No answer."



```{r Data cleaning 2, warning=FALSE}

# Create cleaned data by merging all components
data_clean <- data %>%
  
  # Handle missing values and recode variables
  mutate(
    polintr = ifelse(polintr %in% c(7, 8, 9), NA, polintr),  # Replace invalid responses with NA; How interested in politics.
    lrscale = ifelse(lrscale %in% c(77, 88, 99), NA, lrscale),  # Replace invalid responses with NA; Placement on left right scale. 
    eduyrs = ifelse(eduyrs %in% c(77, 88, 99), NA, eduyrs),    # Replace invalid responses with NA; Years of education. 
    female = ifelse(gndr == 2, 1, 0)  # Recode 'gndr' to 'female' (1 = Female, 0 = Male)
  ) %>%
  
  # Filter out rows where any important variable is NA
  filter(
    !is.na(polintr) &
    !is.na(getavc19) &
    !is.na(agea) &
    !is.na(lrscale) &
    !is.na(eduyrs)
  ) %>%
  
  # Create the 'vaccine_status' variable
  mutate(
    vaccine_status = case_when(
      # Yes, vaccinated or willing
      getavc19 %in% c(1, 2) | getnvc19 %in% c(1) ~ "Yes, vaccinated or willing",

      # No / Refused to answer
      getavc19 %in% c(3, 7) | getnvc19 %in% c(2, 7) ~ "No/Refused to answer",

      # Undecided
      getavc19 %in% c(8, 9) | getnvc19 %in% c(8, 9) ~ "Undecided",

      # Default case (if no match, return NA)
      TRUE ~ NA_character_
    )
  )


```



### Section 3: Explorotary data visualization

We began by visualizing the relationship between vaccination status and voting for far-right parties, controlling for individual political interest, years of education, and country of residence. This initial visualization provided insights into potential patterns and correlations, laying the groundwork for more complex analysis.



```{r Raw data visulization, warning=FALSE, fig.width=12, fig.height=10, fig.align='center'}
data_vi <- data_clean |>
  dplyr::select(polintr, lrscale, eduyrs, gndr, cntry, agea, vaccine_status, far_right_dummy) 

colours <- c(
  'Yes, vaccinated or willing'= "#A26E7C",
  'No/Refused to answer' = "#6681FE",
  'Undecided' = "#1EC98D"
) 

ggplot(data_vi) +
  aes(x = as.factor(polintr), y = eduyrs) +
  geom_point(aes(color = vaccine_status) ,
                 alpha = 0.6, 
                 size = 1.5) +
  facet_grid(rows = vars(far_right_dummy),
             cols = vars(cntry),
             scales = "free_y",
             space = "free_y",
             labeller = labeller(far_right_dummy = c(
                                 "1" = "Vote for far-right party",
                                 "0" = "Other"))) +
  scale_color_manual(values = colours,
                     name = "Vaccine Status") +
  labs(x = "How interested are you in politics", 
       y = "Years of education received",
       title = "Vaccination status and voting for far-right parties controlling for 
       individual political interest, years of education, and country of residence",
       caption = "Data: ESS (European Social Survey), 10th round") +
  theme_minimal() +
  theme(
    plot.title.position = "plot", # left-align title 
    plot.caption.position = "plot", # right-align caption
    legend.position = "top" , # place legend above plot
    plot.title = element_text(face = "bold", size = rel(1.4)) , # larger, bold title
     # monospaced font for axes
    axis.title.x = element_text( #left-aligned, grey x axis label
    hjust = 0,  margin = margin(t = 12)
    ) ,
    legend.text = element_text(size = rel(1)), # larger legend labels
    strip.text = element_text(face = "bold", size = rel(1.15)) , # larger, bold facet labels
    panel.grid.minor = element_blank(),
     plot.background = element_rect(fill = "white", color = "white"),  # White background for plot
    panel.background = element_rect(fill = "white", color = "white"), # White background for panel
    panel.border = element_blank() 
  ) 

```

The raw data visualization indicates that all French (FR) participants selected "Undecided" for their vaccine status, though the reasons for this remain unclear, and their voting choices appeared unrelated. In contrast, participants from Belgium (BG) and Slovenia (SI) exhibited more diverse attitudes toward vaccination, particularly among those voting for non-far-right parties. Participants from Italy (IT), the United Kingdom (GB), and Portugal (PT) demonstrated a more consistent inclination to accept vaccination. Voters aligned with far-right parties showed no discernible trend or consistent stance on vaccination attitudes.



### Section 4: Inferential analysis

We developed a multilevel logistic regression model to examine the the probability of voting for far-right voting on vaccination status, accounting for predictors such as political interest, gender, and years of education. Since not all countries in the survey have identifiable far-right parties, we excluded those without clear far-right representation ("FI", "LT", "ME", "MK"). Additionally, we excluded France from the analysis, as all French respondents were categorized as "Undecided" regarding vaccination—a result we deemed statistically implausible and potentially indicative of data collection issues. Consequently, we removed five countries from the dataset to ensure robust data modeling. We also included survey weights in our model by specifying `weights = data_model$pspwght`. These weights were used to adjust for the unequal probability of selection that often arises in survey data. By using these weights, we ensured that our model's predictions would be representative of the broader population, taking into account different sampling probabilities.



```{r Analysis modelling, warning=FALSE}
# Fit the logistic regression model excluding the 'agea' variable
model_countries <- c("BE", "BG", "CH", "CZ", "EE", "GB", "GR", "HR", 
                     "HU", "IT", "NL", "NO", "PT", "SI", "SK")

data_model <- data_clean[data_clean$cntry %in% model_countries, ] 
data_model$far_right_dummy <- as.factor(data_model$far_right_dummy)
data_model$vaccine_status <- as.factor(data_model$vaccine_status)

model <- glm(far_right_dummy ~ vaccine_status + polintr + female + eduyrs, family = binomial(link = "logit"), data = data_model, weights = data_model$pspwght)

# Calculate robust standard errors using the sandwich package
robust_se <- sqrt(diag(vcovHC(model, type = "HC0")))  

```



### Section 5: Simulation and visualisation 

To gain a deeper understanding, we carried out Monte Carlo simulations across all possible scenarios, given that the data on far-right voting could be limited, particularly for certain vaccination stances. By simulating the model 100,000 times, we ensured that our findings were not simply due to random variation in the data but represented consistent patterns. The simulations allow us to observe how changes in the controls (like political interest, gender, and education level) affect the probability of voting for a far-right party for individuals belonging to each of the three groups based on their stance toward the COVID-19 vaccine: "Undecided," "Yes, vaccinated or willing," and "No, refused."
 
We chose to run the simulations inside the server environment instead of globally to allow for dynamic, user-driven exploration. This way, the simulations are generated in response to user inputs (e.g., country, gender, political interest), enabling real-time updates of the results. Running simulations within the server ensures optimal resource usage, as calculations are performed only when needed, avoiding unnecessary computations. It also allows for personalized predictions based on user-defined scenarios, making the tool interactive and flexible.
 
The plots we generated as a result of these simulations stand for the average predicted probabilities, including confidence intervals that help visualize the uncertainty around these estimates. By doing so, we aimed to optimally represent the impact of each control variable on voting behavior in a way that reveals any potential differences among the three vaccine stance categories.



```{r Simulation visualization 1, warning = FALSE}
# UI definition
ui <- dashboardPage(
  dark = FALSE,
  help = NULL, # Enable dark theme
  dashboardHeader(
    title = "Matei & Liu's Project",
    display = NULL  # Hide the burger and the question mark
  ),
  
  dashboardSidebar(
    sidebarMenu(compact = FALSE,
      # Shorter and clearer title for the sidebar menu
      menuItem("Select Parameters", tabName = "country_plot", icon = NULL)
    ),
    
    # Country Selection Input without duplication
    selectInput("cntry", tagList(icon("globe"), "Select Country:"),
                choices = c("All Countries", "Belgium" = "BE", "Bulgaria" = "BG", "Switzerland" = "CH",
                            "Czech Republic" = "CZ", "Estonia" = "EE", "United Kingdom" = "GB",
                            "Greece" = "GR", "Croatia" = "HR", "Hungary" = "HU", "Italy" = "IT",
                            "Netherlands" = "NL", "Norway" = "NO", "Portugal" = "PT", "Slovenia" = "SI",
                            "Slovakia" = "SK"),
                selected = "All Countries"),
    
    # Gender selection
    selectInput("gndr", tagList(icon("venus-mars"), "Gender:"),
                choices = c("Male" = 0, "Female" = 1),
                selected = 0),
    
    # Dynamic sliders for Political Interest and Years of Education
    uiOutput("polintr_slider"),
    uiOutput("eduyrs_slider"),
    
    # Plot selection with clear configuration
    selectInput("plot_type", tagList(icon("chart-bar"), "Select Plot Type:"),
                choices = c("Predicted Probabilities" = "prob", "Bar Plot" = "bar", "Density Plot" = "other", "Lollipop Plot" = "lollipop", "Box Plot" = "box", "Violin Plot" = "violin")),
    
    # Reset button for all inputs
    actionButton("reset_inputs", "Reset All Inputs", icon = icon("redo"), class = "btn-danger")
  ),
  
  dashboardBody(
    # Body with a dark theme
    tags$head(
      tags$style(HTML(
        ".shiny-input-container, .box {
          transition: transform 0.3s ease-in-out;  /* Only animate transform to prevent darkening */
        }
        .box {
          background-color: #343a40 !important;  /* Set a stable background color */
          color: #f8f9fa;  /* Set text color to maintain visibility */
          border: none !important;  /* Remove border to prevent border color transitions */
          box-shadow: none !important;  /* Remove box-shadow to avoid darkening during animations */
        }
        .fadeIn {
          animation: fadeIn 1s ease-in-out;
        }
        @keyframes fadeIn {
          from { opacity: 1; }
          to { opacity: 1; }  /* Keep opacity constant to avoid any fade effect causing darkening */
        }
        /* Style the slider play buttons */
        .slider-animate-button {
          background-color: #ff0000 !important;  /* Make the play button red */
          border-color: #ff0000 !important;      /* Match border color with button color */
          color: #ffffff !important;             /* Make the play button text white for contrast */
        }"
      ))
    ),
    
    tabItems(
      tabItem(tabName = "country_plot",
              fluidRow(
                # Box to hold the dynamic plot
                box(width = 12, title = "The Predicted Probability of Voting for Far-right Party given the Vaccination Status of Country's Respondents",
                    status = "danger", solidHeader = TRUE,
                    div(style = "animation: fadeIn 1s;", plotOutput("dynamicPlot", height = "calc(70vh)", width = "100%")),  # Responsive plot with 16:9 ratio
                    helpText("Data: ESS (European Social Survey), 10th Round")
                )
              )
      )
    )
  )
)

# Server logic
server <- function(input, output, session) {
  # Toggle sidebar visibility using the burger button
  observeEvent(input$sidebarToggle, {
    js$toggleSidebar()  # Call the JavaScript function to toggle sidebar
  })
  
  # Reset button observer
  observeEvent(input$reset_inputs, {
    updateSelectInput(session, "cntry", selected = "All Countries")
    updateSelectInput(session, "gndr", selected = 0)
    updateSliderInput(session, "polintr", value = mean(reactive_data()$polintr, na.rm = TRUE))
    updateSliderInput(session, "eduyrs", value = mean(reactive_data()$eduyrs, na.rm = TRUE))
    updateSelectInput(session, "plot_type", selected = "prob")
  })
  
  # Reactive dataset based on selected country
  reactive_data <- reactive({
    if (input$cntry == "All Countries") {
      data_clean  # Replace with your data
    } else {
      data_clean %>% filter(cntry == input$cntry)  # Assuming cntry is the country variable
    }
  })
  
  # Dynamic sliders for user input
  output$polintr_slider <- renderUI({
    sliderInput("polintr", tagList(icon("poll"), "Political Interest:"),
                min = min(reactive_data()$polintr, na.rm = TRUE),
                max = max(reactive_data()$polintr, na.rm = TRUE),
                value = mean(reactive_data()$polintr, na.rm = TRUE),
                step = 1, animate = animationOptions(interval = 300, loop = TRUE), ticks = FALSE)
  })
  
  output$eduyrs_slider <- renderUI({
    sliderInput("eduyrs", tagList(icon("graduation-cap"), "Years of Education:"),
                min = min(reactive_data()$eduyrs, na.rm = TRUE),
                max = max(reactive_data()$eduyrs, na.rm = TRUE),
                value = mean(reactive_data()$eduyrs, na.rm = TRUE),
                step = 1, animate = animationOptions(interval = 300, loop = TRUE), ticks = FALSE)
  })
  
  # Reactive Plot based on selected plot type
  output$dynamicPlot <- renderPlot({
    
    # Extract coefficients from the model (example model)
    coef_estimates <- coef(model)  # Assuming 'model' is your model object
    vcov_matrix <- vcovHC(model, type = "HC3")  # Use robust covariance matrix
    
    # Monte Carlo simulations (100,000 draws) for uncertainty
    n_sim <- 100000
    simulated_coefs <- mvrnorm(n_sim, mu = coef_estimates, Sigma = vcov_matrix)
    
    # Prediction data
    prediction_data <- data.frame(
      vaccine_status = c("Yes, vaccinated or willing", "No/Refused to answer", "Undecided"),
      polintr = as.numeric(input$polintr),
      female = as.numeric(input$gndr),
      eduyrs = as.numeric(input$eduyrs)
    )
    
    # Simulate probabilities
    simulations <- do.call(rbind, lapply(1:nrow(prediction_data), function(i) {
      X <- c(
        1,  # Intercept
        as.numeric(prediction_data$vaccine_status[i] == "Undecided"),
        as.numeric(prediction_data$vaccine_status[i] == "Yes, vaccinated or willing"),
        prediction_data$polintr[i],
        prediction_data$female[i],
        prediction_data$eduyrs[i]
      )
      probs <- 1 / (1 + exp(-simulated_coefs %*% X))
      data.frame(vaccine_status = prediction_data$vaccine_status[i], prob = probs)
    }))
    
    # Summarize simulations
    simulation_summary <- simulations %>%
      group_by(vaccine_status) %>%
      summarise(
        mean_prob = mean(prob),
        lower_ci = quantile(prob, 0.025),
        upper_ci = quantile(prob, 0.975)
      )
    
    # Plot selection based on input
    plot_width <- session$clientData$output_dynamicPlot_width  # Get plot width
    plot_height <- plot_width * 0.625  # 16:10 aspect ratio 
    
    # Set scaling factor based on plot size
    scaling_factor <- max(10, plot_width / 600)  # Adjust scaling factor based on width
    
    # Color Universal Design (CUD) color palette for colorblind-friendly colors
    cud_colors <- c("#E69F00", "#56B4E9", "#009E73", "#F0E442", "#0072B2", "#D55E00")
    
    # Plot generation
    if (input$plot_type == "prob") {
      ggplot(simulation_summary, aes(x = vaccine_status, y = mean_prob * 100, fill = vaccine_status)) +
        geom_point(aes(color = vaccine_status), size = 5) +  # Adding color for points
        scale_color_manual(values = cud_colors) +  # Apply CUD color palette
        geom_errorbar(aes(ymin = lower_ci * 100, ymax = upper_ci * 100), width = 0.2, color = "#888888") +
        labs(x = "Vaccination Status", y = "Predicted Probability (%)") +  # Removed 'fill' in the legend
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_minimal() +
        theme(
          axis.text = element_text(size = 1.5 * scaling_factor),
          axis.title = element_text(size = 1.7 * scaling_factor, face = 'bold', margin = margin(t = 10, r = 10, b = 10, l = 10)),
          plot.title = element_text(size = 2 * scaling_factor),
          legend.position = "none",  # Removes the legend completely
          legend.text = element_text(size = 1.2 * scaling_factor, face = 'bold'),
          legend.title = element_text(size = 1.7 * scaling_factor, face = 'bold')
        )
      
    } else if (input$plot_type == "bar") {
      ggplot(simulation_summary, aes(x = vaccine_status, y = mean_prob * 100, fill = vaccine_status)) +
        geom_bar(stat = "identity") +
        geom_errorbar(aes(ymin = lower_ci * 100, ymax = upper_ci * 100), width = 0.2, color = "#888888", position = position_dodge(0.9)) +
        scale_fill_manual(values = cud_colors) +  # Apply CUD color palette to bars
        labs(x = "Vaccination Status", y = "Predicted Probability (%)", fill = "Vaccination Status") +
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_minimal() +
        theme(
          axis.text = element_text(size = 1.5 * scaling_factor),
          axis.title = element_text(size = 1.7 * scaling_factor, face = 'bold', margin = margin(t = 10, r = 10, b = 10, l = 10)),
          plot.title = element_text(size = 2 * scaling_factor),
          legend.text = element_text(size = 1.2 * scaling_factor, face = 'bold'),
          legend.title = element_text(size = 1.7 * scaling_factor, face = 'bold')
        ) +
        guides(fill = guide_legend(title = "COVID-19 Vaccination Status"))
      
    } else if (input$plot_type == "lollipop") {
      ggplot(simulation_summary, aes(x = vaccine_status, y = mean_prob * 100)) +
        geom_segment(aes(x = vaccine_status, xend = vaccine_status, y = 0, yend = mean_prob * 100), color = "#888888", size = 1) +
        geom_point(aes(color = vaccine_status), size = 5) +  # Adding color for points
        scale_color_manual(values = cud_colors) +  # Apply CUD color palette
        labs(x = "Vaccination Status", y = "Predicted Probability (%)") +  # Removed 'fill' in the legend
        scale_y_continuous(labels = scales::percent_format(scale = 1)) +
        theme_minimal() +
        theme(
          axis.text = element_text(size = 1.5 * scaling_factor),
          axis.title = element_text(size = 1.7 * scaling_factor, face = 'bold', margin = margin(t = 10, r = 10, b = 10, l = 10)),
          plot.title = element_text(size = 2 * scaling_factor),
          legend.position = "none",  # Removes the legend completely
          legend.text = element_text(size = 1.2 * scaling_factor, face = 'bold'),
          legend.title = element_text(size = 1.7 * scaling_factor, face = 'bold')
        )
      
    } else if (input$plot_type == "box") {
      ggplot(simulations, aes(x = vaccine_status, y = prob * 100, fill = vaccine_status)) +
        geom_boxplot() +
        scale_fill_manual(values = cud_colors) +
        labs(x = "Vaccination Status", y = "Predicted Probability (%)", fill = "Vaccination Status") +
        theme_minimal() +
        theme(
          axis.text = element_text(size = 1.5 * scaling_factor),
          axis.title = element_text(size = 1.7 * scaling_factor, face = 'bold', margin = margin(t = 10, r = 10, b = 10, l = 10)),
          plot.title = element_text(size = 2 * scaling_factor),
          legend.text = element_text(size = 1.2 * scaling_factor, face = 'bold'),
          legend.title = element_text(size = 1.7 * scaling_factor, face = 'bold')
        )
      
    } else if (input$plot_type == "violin") {
      ggplot(simulations, aes(x = vaccine_status, y = prob * 100, fill = vaccine_status)) +
        geom_violin(trim = FALSE) +
        scale_fill_manual(values = cud_colors) +
        labs(x = "Vaccination Status", y = "Predicted Probability (%)", fill = "Vaccination Status") +
        theme_minimal() +
        theme(
          axis.text = element_text(size = 1.5 * scaling_factor),
          axis.title = element_text(size = 1.7 * scaling_factor, face = 'bold', margin = margin(t = 10, r = 10, b = 10, l = 10)),
          plot.title = element_text(size = 2 * scaling_factor),
          legend.text = element_text(size = 1.2 * scaling_factor, face = 'bold'),
          legend.title = element_text(size = 1.7 * scaling_factor, face = 'bold')
        )
      
    } else {
      ggplot(simulations, aes(x = prob, fill = vaccine_status)) +
        geom_density(alpha = 0.4) +
        scale_fill_manual(values = cud_colors) +  # Apply CUD color palette to density plot
        labs(x = "Predicted Probability", y = "Density", fill = "Vaccination Status") +
        theme_minimal() +
        theme(
          axis.text = element_text(size = 1.5 * scaling_factor),
          axis.title = element_text(size = 1.7 * scaling_factor, face = 'bold', margin = margin(t = 10, r = 10, b = 10, l = 10)),
          plot.title = element_text(size = 2 * scaling_factor),
          legend.text = element_text(size = 1.2 * scaling_factor, face = 'bold'),
          legend.title = element_text(size = 1.7 * scaling_factor, face = 'bold')
        ) +
        guides(fill = guide_legend(title = "COVID-19 Vaccination Status"))
    }
  })
}

# Run the Shiny app
shinyApp(ui = ui, server = server, options = list(launch.browser = TRUE, width = 1200, height = 800))

```
